\bf ``A p-value of $<$ 0.05 was considered statistically significant'': a content analysis of published statistical methods sections

### 2021-07-12 manuscript/asa_template/asa_template_almostdone.tex
update tex file

Figure \ref{fig:anzctr-wordclouds} shows word clouds for the ten topics identified by the NMF algorithm. 
Words related to the largest topic (topic 2, n = 1,834) reflected descriptions of sample size calculations, for example, ``sample'',``power'' and ``80'' (i.e. $80\%$ power) . Other topics indicated pilot studies (topic 5, n = 834),
safety/tolerability studies (topic 6, n = 524), descriptive statistics (topic 7, n = 333),
intervention studies (topic 8, n = 1020) and repeated measures ANOVA (topic 10 = 852). A review of word counts by topic 
identified statistical methods sections that were only one word, including ``ANOVA'',
``t-test'', ``SPSS'' and even ``SSPS''.

>>>>

Figure \ref{fig:anzctr-wordclouds} shows word clouds for the ten topics identified by the NMF algorithm. 
Words related to the largest topic (topic 2, n = 1,834) reflected descriptions of sample size calculations, for example, ``sample'',``power'' and ``80'' (i.e. $80\%$ power) . Other topics indicated pilot studies (topic 5, n = 834),
safety/tolerability studies (topic 6, n = 524), descriptive analysis (topic 7, n = 333),
intervention studies (topic 8, n = 1020) and repeated measures ANOVA (topic 10 = 852). A review of word counts by topic 
identified statistical methods sections that were only one word, including ``ANOVA'',
``t-test'', ``SPSS'' and even ``SSPS''.
